---
title: "In-Class Work"
output: html_document
date: "2023-02-06"
---
# in_class_work

example_vec = c("chuck", "chris", "karen")

class(example_vec)
typeof(example_vec)

named_vec = c("football_bro" = "chuck",
              "actor" = "chris",
              "unpleasant" = "karen")

str(named_vec)
# change names to attribute names
names(example_vec) = c(1,2,3)
attr(example_vec, "names") = c("lol", "rofl", "ftw")

example_vec
# added an attribute
attr(example_vec, "gibberish") = c("lol", "rofl", "ftw")

example_vec

# -----lists 

test_list = list("letters" = letters,
                 "numbers" = 1:26)

test_list

# now it gets weird haha 

attr(test_list, "class") = "data.frame"
attr(test_list, "row.names") = 1:26

test_list
# outturn: we tricked R into thinking that the earlier list test_list is data frame now! 


--------
#  DAY 5 - FUNCTIONS 
### 06.02.2023
  
num_vec = c(3, 12, 7, 9, 27, 21, 3)

mode(num_vec)

get_mode = function(...){
  
  #unlist all input to find mode
  flat = unlist(...)
  
  #find the most common input 
  mode_table = table(flat)
  
  #
}

#--schmierblatt aufg 

num_vec
#### [1]  3 12  7  9 27 21  3

test = table(num_vec)

max(test)
#### [1] 2

names(test)
#### [1] "3"  "7"  "9"  "12" "21" "27"

test["7"]

test = table(num_vec)


vec_2 = c(11, 57, 42, 11, 21, 2) 
get_mode(num_vec, vec_2)




# Question 2 

```{r}
survey$pets
```

```{r}
### create output function 

pet_output = data.frame(
  "id" = 1:nrow(survey),
  "dog" = NA,
  "cat" = NA,
  "fish" = NA,
  "bird" = NA,
  "reptile" = NA,
  "rock" = NA,
  "none" = NA,
  "other" = NA)

```

```{r} 
### TRUE / FALSE value check for dogs 
grepl(pattern = "dog", x = survey$pets, ignore.case = TRUE)

#### We can see that whenever the term "dog" appears as a value the grepl output shows "TRUE" instead of "FALSE". 
```

#----- 8.2.23 DEBUGGING 

# DEBUG 1
```{r}
example = c(1, 2, 3, 3, 4, 5, 7)

error_example = function(numeric_vector) {
  
  # Sum it up!
  vec_sum = sum(example)
  
  # divide by sum!
  percents = example / vec_sum
  
  # Get a table!
  vec_table = table(example)
  
  # Sum the possibilities!
  sum_names = sum(as.numeric(names(vec_table)))
  
  # return the table!
  return(vec_table)
}

error_example(example)
```

```{r}
traceback()
```

```{r}
debugonce(error_example)
```

```{r}
# debug window opens:
# type n = next; R will run the next code (you can check in the environment tab the output)
# issue here: names cannot be summed because they're characters - fixed: as.numeric in front of it
# to stop browsing: click on stop; comment browse!
```


# DEBUG 2

```{r}
# Make example
example1 = c(1, 2, 3, 3, 4, 5, 7)
example2 = c(5, 5, 5, 5, 5, 5, 5)

# re-create my failed mode from Monday
get_mode = function(...){
  
  # unlist all input to find mode
  flat = unlist(list(...))
  
  # find the most common input
  mode_table = table(flat)
  
  # get hte name of the most common element
  our_mode = names(which.max(mode_table))
  
  # return output
  return(our_mode)
}

# Bad result!
get_mode(example1, example2)
```

```{r}
#issue here: unlist only takes the first vector (because unlist as a function only takes one argument - fixed: put list(...) inside unlist)
```

