---
title: "git_worksheet_2_objects_in_r"
output: html_document
date: "2023-02-01"
editor_options: 
  chunk_output_type: inline
---

### Q1: Predict class of vectors

#### A: 1: numeric, 2: character, 3: character, 4: numeric

```{r}
# example 1
q1_1 <- c(TRUE, 8)

# example 2
q1_2 <- c("TRUE", FALSE)

# example 3
q1_3 <- c(F, F, F, T)

# example 4
q1_4 <- c(TRUE, TRUE, TRUE, 1)
```

```{r}
class(q1_1)
class(q1_2)
class(q1_3)
class(q1_4)
```

#### number 3 isn't a character, it's logical (I thought False and True have to be written out, but the letters are also not in quotation marks... gotta be more careful)

### Q2: What will happen with the following code? 

```{r}
as.numeric(c("Will", "I", "work?"))
```

#### A: The code shouldn't work, because this isn't a factor. Therefore the vector stays with the characters. 

```{r}
as.numeric(c("Will", "I", "work?"))
```

### Q3: What happens here? 

```{r}
test_vec = c(1, 3, 3, 7)
class(test_vec) = "character"
```

#### A: The vector entails numeric objects in the beginning, however, the second code changes the class type and made the vector have character objects now. If we run test_vec we get the following: 

```{r}
test_vec
```

### Q4: Add another attribute 
```{r}
# make a named vector (weather forecast in degrees F)
named_vec = c("Mon" = 39, "Tues" = 36, "Wed" = 44, "Thur" = 36, "Fri" = 44, "Sat" = 45, "Sun" = 37)
named_vec
```

```{r}
# quick maths
named_vec * 2
```

```{r}
str(named_vec)
```

```{r}
attr(named_vec, "month/day") = "01/30, 01/31, 02/01, 02/02, 02/03, 02/04, 02/05"  
```

```{r}
attributes(named_vec)
```
### Q5: Subsetting

```{r}
# get the built in mtcars data
cars = mtcars

# subset using $
mtcars$mpg
```

```{r}
# subset using []
mtcars[, "mpg"]
```

```{r}
# make an example list to work with
example_list = list("numbers" = c(1, 2, 5, 7, 3, 5),
                    "letters" = c("y", "u", "n", "r", "t", "b"),
                    "df" = mtcars)
```

```{r}
# get element 1
example_list[1]
```

```{r}
# get contents of element 1
example_list[[1]]
```

```{r}
# using $
example_list$numbers
```

```{r}
# using name
example_list[["numbers"]]
```

```{r}
# using position
example_list[[1]]
```

```{r}
# subset number 7 from the number vector 
example_list$numbers[4]
```

```{r}
# subset letters y and t from the character vector
example_list$letters[c(1,5)] 
```

#### ? I don't know hoe to subset both letters together... 

```{r}
# subset entire mtcars dataframe
example_list$df
```

